### 2021-03-20 papers.tex
added keywords

\addtrack
	{}{Big Dummy Track}
\addpaper
	{Refutation of the “Failure to remove the template text from your paper may result in your paper not being published” Conjecture}
	{Nicolas Hurtubise}
	{Keywords: anonymous, triple blind, review}
	{SIGBOVIK_2021_paper_1}
	{0cm}
	{}
\addpaper
	{Stop Doing Type Theory}
	{Jason Reed}
	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_2}
	{0cm}
	{}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}
	{SIGBOVIK_2021_paper_10}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

@@

	{Keywords: peer review, SotA, State-of-the-Art, computer vision, machine learning}

>>>>

\addtrack
	{}{Big Dummy Track}
\addpaper
	{Refutation of the “Failure to remove the template text from your paper may result in your paper not being published” Conjecture}
	{Nicolas Hurtubise}
	{Keywords: component, formatting, style, styling, insert}
	{SIGBOVIK_2021_paper_1}
	{0cm}
	{}
\addpaper
	{Stop Doing Type Theory}
	{Jason Reed}
	{Keywords: Ranting, Raving, Muttering, Grumbling}
	{SIGBOVIK_2021_paper_2}
	{0cm}
	{}

@@

	{Keywords: SIGBOVIK, Statistics, Finality}

@@

	{Keywords: covid, bovik, short}

@@

	{Keywords: Almost Monopoly, AlphaX, Artificial Neural Networks, Board Games, Deep Learning, Games With Boards, Machine Learning, Machine Learning That Matters, Reinforcement Learning, Tree Search}

@@

	{Keywords: PvsNP, Max_Independent_Set, TCS, Algorithms}

@@

	{Keywords: damn, forgot, again, deadlines}

@@

	{Keywords: Machine learning, embedding, auto-encoders, Zalgo he comes, dimensional reduction}

@@

	{Keywords: best, paper, award}

@@

	{Keywords: artificial intelligence, ethics, machine learning}

@@

	{Keywords: Plant powered science, AI, Scientific method, Survey}

@@

	{Keywords: mortal-kombat, truth, meaning-of-life}

@@

	{Keywords: Unicode, magic trick, emojis, bitwise operators, sleight of bits}

@@

	{Keywords: recursion, stone tools, computer science, handaxe, processor, prehistory, palaeogaming, psychedelic pragmatism}

@@

	{Keywords: CSRankings, computer science rankings, bad proxies for quality, research quality, ego stroking, navel gazing, ranking algorithms}

@@

	{Keywords: deep learning, recaptcha, automation, david}

@@

	{Keywords: machine learning, reinforcement learning, gradient, do these appear anywhere?}

@@

	{Keywords: font, video game, font video game, silly idea done seriously}

@@

	{Keywords: busy beaver, computability, turing machines, algorithms, breadboards, TTL, MacBook Pro}

@@

	{Keywords: Maximization, Information Theory, Complexity, Divine Intervention, Academic Integrity, Big Small, Does Anybody Read These Things?}

@@

	{Keywords: types, databases, constraints, texting, machine translation, typescript}

@@

	{Keywords: yoko ono, instruction programs, art jokes, one page papers}

@@

	{Keywords: Tenet, Inverted, Temporal Pincer, Entropy, Turnstile, Inverted Code Theory, P vs. NP, Quantum Computing, Reinforcement Learning}

@@

	{Keywords: lottery, random, language models}
